Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-12 paper.tex
ADD GJR citation

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most economically intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables are indeed predictive, one may test the significance of coefficients in a regression of the supposedly predictive variable onto equity market returns. The most straightforward way of doing this is via the t-test. \citet{elliott1994inference} find that this test has a nonstandard distribution under the null if the largest autoregressive root of the regressor is close to unity and the innovations of regressor and regressand are correlated. Given the presence of these nuisances, the t-test will lead to invalid inference. In this context, \citet{campbell2006efficient} develop a test that exploits information about the autoregressive root of the regressor and thus tries to overcome this issue. Section $\ref{regression}$ formalizes the regression setup and outlines the problem. Section $\ref{Derivation of the tests}$ explains the derivation of the Campbell and Yogo's (2006) test. This is done by first considering optimal tests, albeit under unrealistic assumptions, in section $\ref{Infeasible tests}$. This section also establishes the conditions for a nonstandard distribution of the t-statistic. A pretest based on these conditions is described in section $\ref{pretest}$. Section $\ref{Making the Q-test feasible}$ details the use of Bonferroni's inequality in making the test feasible.  The test is further generalized to more realistic assumptions in section $\ref{implementation}$ and its mathematical implementation is described. Section $\ref{power}$ summarizes the power advantages of the test found by \citet{campbell2006efficient}. Section $\ref{Monte Carlo simulation}$ proceeds with evaluating finite-sample rejection rates of the feasible Q-test under various innovation distributions and violations of assumptions made in section $\ref{implementation}$. First, Monte Carlo evidence of \citet{campbell2006efficient} is scrutinized and replicated in section $\ref{Simulation with Gaussian innovations}$. Section $\ref{Simulation with weakly persistent regressors and Gaussian innovations}$ demonstrates over-rejection in finite-samples when the largest autoregressive root of the regressor is nonlocal-to-unity. An attempt of modeling innovations by a multivariate GARCH process is then made in section $\ref{Simulation with CCC-GARCH innovations}$. This is further refined in section $\ref{Simulation with common GARCH innovations}$ where it is hypothesized that innovation variances of both the regressor and the regressand share a common stochastic trend that is modeled by a GARCH process. Section $\ref{Simulation with common GJR-GARCH innovations}$ concludes the Monte Carlo evidence by simulation of the common stochastic trend by GJR-GARCH with conditional leptokurtosis. Empirical findings are replicated and evaluated on out-of-sample data in section $\ref{Empirical Results}$. Finally, section $\ref{conclusion}$ concludes.

@@

To reason about how to incorporate information about $\rho$ into the test \citet{campbell2006efficient} assume $\rho$ to be known at first. If, further, the assumption $\alpha=\gamma=0$ is made, the only unknown variable that remains is $\beta$. Now, the likelihood function can be denoted as $L(\beta)$. If one restricts oneself to consider only the simple alternative of the form $\beta=\beta_{1}$ one can reason by the Neyman–Pearson Lemma that the most powerful test is of the form
\begin{equation}
\begin{aligned} \sigma_{u}^{2}\left(1-\delta^{2}\right)\left(L\left(\beta_{1}\right)-L\left(\beta_{0}\right)\right)=& 2\left(\beta_{1}-\beta_{0}\right) \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right] \\ &-\left(\beta_{1}^{2}-\beta_{0}^{2}\right) \sum_{t=1}^{T} x_{t-1}^{2}>C, \end{aligned}
\end{equation}
with $\beta_{u e}=\sigma_{u e} / \sigma_{e}^{2}$ and $C$ being some constant.
This optimal test is not uniformly most powerful [UMP], however, since it is a weighted sum of minimal sufficient statistics and the weights depend on $\beta_{1}$. For that reason, \citet{campbell2006efficient} propose to condition the test on the ancillary statistic  $\sum_{t=1}^{T} x_{t-1}^{2}$. As a result the test can be simplified to
\begin{equation}
 \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]>C,
\end{equation}
which is UMP for alternatives of the form $\beta_{1}>\beta_{0}$ when $\rho$ is known.

@@

If this confidence interval does not contain zero, the regressor is inferred to have predictive power. While this test is valid, it is conservative, however, since Bonferroni's inequality is likely to be strict, i.e., the coverage of $C_{\beta}(\alpha)$ is likely greater than $100(1-\alpha) \%$. For that reason, \citet{campbell2006efficient} refine the confidence interval based on a numerical method proposed by Cavanagh et al. (1995). To obtain a tighter confidence interval with significance level $\widetilde{\alpha}$, according to this method, $\alpha_{2}$ is fixed first. $\operatorname{Pr}\left(\underline{\beta}\left(\overline{\rho}\left(\overline{\alpha}_{1}\right), \alpha_{2}\right)>\beta\right)$ is then evaluated for each $\delta$, and $\overline{\alpha}_{1}$ is selected such that 

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
Glosten, Jagannathan and Runkle (1993) [GJR] observe that in financial markets negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the square of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$ negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%.

>>>>

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most economically intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables are indeed predictive, one may test the significance of coefficients in a regression of the supposedly predictive variable onto equity market returns. The most straightforward way of doing this is via the t-test. \citet{elliott1994inference} find that this test has a nonstandard distribution under the null if the largest autoregressive root of the regressor is close to unity and the innovations of regressor and regressand are correlated. Given the presence of these nuisances, the t-test will lead to invalid inference. In this context, \citet{campbell2006efficient} develop a test that exploits information about the autoregressive root of the regressor and thus tries to overcome this issue. Section $\ref{regression}$ formalizes the regression setup and outlines the problem. Section $\ref{Derivation of the tests}$ explains the derivation of Campbell and Yogo's (2006) test. This is done by first considering optimal tests, albeit under unrealistic assumptions, in section $\ref{Infeasible tests}$. This section also establishes the conditions for a nonstandard distribution of the t-statistic. A pretest based on these conditions is described in section $\ref{pretest}$. Section $\ref{Making the Q-test feasible}$ details the use of Bonferroni's inequality in making the test feasible.  The test is further generalized to more realistic assumptions in section $\ref{implementation}$ and its mathematical implementation is described. Section $\ref{power}$ summarizes the power advantages of the test found by \citet{campbell2006efficient}. Section $\ref{Monte Carlo simulation}$ proceeds with evaluating finite-sample rejection rates of the feasible Q-test under various innovation distributions and violations of assumptions made in section $\ref{implementation}$. First, Monte Carlo evidence of \citet{campbell2006efficient} is scrutinized and replicated in section $\ref{Simulation with Gaussian innovations}$. Section $\ref{Simulation with weakly persistent regressors and Gaussian innovations}$ demonstrates over-rejection in finite-samples when the largest autoregressive root of the regressor is nonlocal-to-unity. An attempt of modeling innovations by a multivariate GARCH process is then made in section $\ref{Simulation with CCC-GARCH innovations}$. This is further refined in section $\ref{Simulation with common GARCH innovations}$ where it is hypothesized that innovation variances of both the regressor and the regressand share a common stochastic trend that is modeled by a GARCH process. Section $\ref{Simulation with common GJR-GARCH innovations}$ concludes the Monte Carlo evidence by simulation of the common stochastic trend by GJR-GARCH with conditional leptokurtosis. Empirical findings are replicated and evaluated on out-of-sample data in section $\ref{Empirical Results}$. Finally, section $\ref{conclusion}$ concludes.

@@

To reason about how to incorporate information about $\rho$ into the test \citet{campbell2006efficient} assume $\rho$ to be known at first. If, further, the assumption $\alpha=\gamma=0$ is made, the only unknown variable that remains is $\beta$. Now, the likelihood function can be denoted as $L(\beta)$. If one restricts oneself to consider only the simple alternative of the form $\beta=\beta_{1}$ one can reason by the Neyman–Pearson Lemma that the most powerful test is of the form
\begin{equation}
\begin{aligned} \sigma_{u}^{2}\left(1-\delta^{2}\right)\left(L\left(\beta_{1}\right)-L\left(\beta_{0}\right)\right) = & 2\left(\beta_{1}-\beta_{0}\right) \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right] \\ &-\left(\beta_{1}^{2}-\beta_{0}^{2}\right) \sum_{t=1}^{T} x_{t-1}^{2}>C, \end{aligned}
\end{equation}
with $\beta_{u e}=\sigma_{u e} / \sigma_{e}^{2}$ and $C$ being some constant.
This optimal test is not uniformly most powerful [UMP], however, since it is a weighted sum of minimal sufficient statistics and the weights depend on $\beta_{1}$. For that reason, \citet{campbell2006efficient} propose to condition the test on the ancillary statistic  $\sum_{t=1}^{T} x_{t-1}^{2}$. As a result the test can be simplified to
\begin{equation}
 \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]>C,
\end{equation}
which is UMP for alternatives of the form $\beta_{1}>\beta_{0}$ when $\rho$ is known.

@@

If this confidence interval does not contain zero, the regressor is inferred to have predictive power. While this test is valid, it is conservative, however, since Bonferroni's inequality is likely to be strict, i.e., the coverage of $C_{\beta}(\alpha)$ is likely greater than $100(1-\alpha) \%$. For that reason, \citet{campbell2006efficient} refine the confidence interval based on a numerical method proposed by \citet{cavaliere2005unit}. To obtain a tighter confidence interval with significance level $\widetilde{\alpha}$, according to this method, $\alpha_{2}$ is fixed first. $\operatorname{Pr}\left(\underline{\beta}\left(\overline{\rho}\left(\overline{\alpha}_{1}\right), \alpha_{2}\right)>\beta\right)$ is then evaluated for each $\delta$, and $\overline{\alpha}_{1}$ is selected such that 

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
\citet*{glosten1993relation} [GJR] observe that in financial markets negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the square of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$ negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%.
